---
title: "Final Project - EPI 590r"
author: "Santino Diaz-Palma"
format: html
	echo: false
---
For my final project, I chose a datset from tidyRainbow Datasets. It contains information about LGBTQ+ movies and their popularity. My goal is to find out what language is most common amongst the popular movies!  
```{r}
#Lets read in our libraries and the dataset. This section will be hidden from output because
# that is not something we need to include in our report. Additionally, we will clean the data. 
# Additionally, I anticipate removing overview and genre_ids from the dataset due to them
# 	not necessarily being needed to answer my research question(s)
#| echo: false
#| warning: false
#| message: false
library(tidyverse)
library(broom)
library(gtsummary)
library(here)

lgbtq_cols <- c("id","title","original_title","original_language","overview", "release_date",
								"popularity", "vote_average", "vote_count", "adult", "video", "genre_ids")

lgbtq <- read_csv(here::here("Data", "movieData.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
									skip = 1, 
									col_names = lgbtq_cols,
									col_select = -c("overview","genre_ids"))
#Lets create some more intuitive levels for our categorical variables
|>
	mutate(adult_cat = factor(adult, labels = c("Yes", "No")),
				 sex_cat = factor(sex, labels = c("Male", "Female")),
				 race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
				 eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
				 glasses_cat = factor(glasses, labels = c("No", "Yes")))

#Lets check our NA values and see if were missing anything or need to do cleans
str(lgbtq)

## Create folder for clean data (if it doesn't exist already)
if (!dir.exists(here::here("data", "clean"))) {
	dir.create(here::here("data", "clean"))
}

## Save complete data in (newly made) folder
write_rds(lgbtq, here::here("data", "clean", "lgbtq_clean.rds"))
```

For the final project, I will orient this file by the specific objectives we have to achieve. 
Thus, let's begin with number 1: *Create a {gtsummary} table of descriptive statistics about your data (1 pt

```{r}




```





