---
title: "Final Project - EPI 590r"
author: "Santino Diaz-Palma"
format: html
echo: false
---

```{r}
#| echo: false
#| warning: false
#| message: false
#| output: false

#Lets read in our libraries and the dataset. This section will be hidden from output because
# that is not something we need to include in our report. Additionally, we will clean the data. 
# Additionally, I anticipate removing overview and genre_ids from the dataset due to them
# 	not necessarily being needed to answer my research question(s)
library(tidyverse)
library(broom)
library(gtsummary)
library(here)

#load in clean data
lgbtq_cols <- c("id","title","original_title","original_language","overview", "release_date",
								"popularity", "vote_average", "vote_count", "adult", "video", "genre_ids")
languages_above_100 <- c("en", "de", "fr", "it", "ja", "es", "pt")
lgbtq <- read_csv(here::here("Data", "movieData.csv"),
									na = c("-1", "-2", "-3", "-4", "-5", "-998", "xx"),
									skip = 1,
									col_names = lgbtq_cols,
									col_select = -c("overview","genre_ids")) |>
	mutate(original_language = as.factor(original_language)) |>
	mutate(original_language = ifelse(original_language %in% languages_above_100,
																		as.character(original_language), "Other")) |>
	mutate(adult = factor(adult, labels = c("No", "Yes")),
				 video = factor(video, labels = c("No", "Yes")),
				 original_language = factor(original_language, labels =
				 													 	c("German",
				 													 		"English",
				 													 		"French",
				 													 		"Italian",
				 													 		"Japanese",
				 													 		"Spanish",
				 													 		"Other",
				 													 		"Portuguese")))

#### In-line Texts
lgbtq_stats <- list(n = nrow(lgbtq),
              			mean_popul = mean(lgbtq$popularity, na=TRUE))
```

[**Description of my dataset:**]{.underline}

For my final project, I chose a datset from tidyRainbow Datasets. It contains information about LGBTQ+ movies (n=`r lgbtq_stats$n`) and their popularity. My goal is to find out what language is most common among LGBTQ+ movies! 

*Please see the readme file for more details concerning instructions, coding, and inclusion/exclusion criteria.*


I've oriented this document to showcase the specific objectives required by the project guidelines. Starting with our **first objective**, let's create a table of descriptive statistics about the data (aka the infamous @tbl-descr). 
*NOTE: This table is stratified by designation of being an Adult Film or not*

```{r}
#| warning: false
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide

table1 <- tbl_summary(
	lgbtq,
	by = adult,
	include = c(
		popularity, vote_average, original_language,
		vote_count, video
	),
	label = list(
		popularity ~ "Popularity",
		vote_average ~ "Average Votes",
		original_language ~ "Language of Film",
		vote_count ~ "Vote Count",
		video ~ "Video"
	),
	missing_text = "Missing"
) |>
add_p(test = list(
	all_continuous() ~ "t.test",
	all_categorical() ~ "chisq.test"
)) |>
	# add a total column with the number of observations
	add_overall(col_label = "**Total** N = {N}") |>
	bold_labels() |>
	# remove the default footnotes
	modify_footnote(update = everything() ~ NA) |>
	# replace the column headers and make them bold
	modify_header(label = "**Variable**", p.value = "**P-value**")


#in-line stats
table1
pop_total <- inline_text(table1, 
                           variable = "popularity", 
                           column = "stat_0")
```

Our **second objective** will be to create a linear regression model (known as @tbl-regression). I've chosen popularity as my outcome, with three predictors (the original language of the film, adult status, and average vote). For reference, the total popularity is `r pop_total`.

```{r}
#| label: tbl-regression
#| tbl-cap: "Linear Regression Model Statistics"
#| output-location: slide
#Linear Model
linear_model <- lm(popularity ~ original_language + adult + vote_average,
	data = lgbtq
)
tbl_regression(
	linear_model,
	# include the intercept
	intercept = TRUE,
	# relabel the variables
	label = list(
		original_language ~ "Language of Film",
		vote_average ~ "Average Number of Votes",
		adult ~ "Adult film (y/n)"
	)
) |>
	modify_header(label = "**Variable**", p.value = "**P-value**")

```

The **3rd objective** is to create a @fig-barplot that represents some aspect of the dataset. I chose to showcase which languages have the most LGBTQ+ films using a bar plot.  

```{r}
#| label: fig-barplot
#| fig-cap: "Most Popular Languages amongst LGBTQ+ Films"
#Figure 1
lang_freq_table <- table(lgbtq$original_language)
lang_data <- as.data.frame(lang_freq_table)
names(lang_data) <- c("Language","Number of Films")
ggplot(lang_data, aes(x = Language, y = `Number of Films`)) +
	geom_bar(stat = 'identity', fill = 'skyblue') +
	labs(title = 'Most Popular Languages amognst LGBTQ+ films', x = 'Language', 
			 y ='Number of Films') +
	theme_minimal() +
	theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

In conclusion, we can see that English is the most popular langauge for LGBTQ+ films. 
